The ChEMBL database as Linked Open Data

### 2012-03-05 article.tex
Added a diagram showing the data structures in the data
Reordered author details
Completer address

\usepackage[T1]{fontenc}
\usepackage{times}%
\usepackage{natbib}% for bibliography sorting/compressing
%\usepackage{amsmath}
%\usepackage{endnotes}
%\usepackage{graphics}

@@

\bibliographystyle{plain}

@@

% For one author:
\author[A]{\fnms{Egon} \snm{Willighagen}} % \thanks{Huh?}}
\address[A]{Maastricht University}
\runningauthor{E.L. Willighagen et al.}

% Two or more authors (order to be determined):
\author[B]{\fnms{Ola} \snm{Spjuth}},
\address[B]{Uppsala University}

\author[C]{\fnms{Peter} \snm{Ansell}},
\address[C]{xxx}

\author[D]{\fnms{Antony} \snm{Williams}},
\address[D]{xxx}

\author[E]{\fnms{John} \snm{Overington}},
\author[E]{\fnms{Anna} \snm{Gaulton}},
\address[E]{European Bioinformatics Institute}

%\author[B]{\fnms{} \snm{}}
%\runningauthor{}
%\address[A]{}

@@

%\begin{figure}[t]
%\includegraphics{}
%\caption{Figure caption.}\label{f1}
%\end{figure}

@@

% \printbibliography

>>>>

\usepackage[T1]{fontenc}
\usepackage{times}%
\usepackage{natbib}% for bibliography sorting/compressing
%\usepackage{amsmath}
%\usepackage{endnotes}
\usepackage{graphicx}
%\usepackage{tikz}
%\usetikzlibrary{snakes,arrows,shapes}

@@

% \bibliographystyle{plain} 
\bibliographystyle{unsrt}

@@

% For one author:
\author[A]{\fnms{Egon} \snm{Willighagen}\thanks{Corresponding author.\\ E-mail: egon.willighagen@maastrichtuniversity.nl.}}
% Two or more authors (order to be determined):
\author[B]{\fnms{Ola} \snm{Spjuth}},
\author[C]{\fnms{Peter} \snm{Ansell}},
\author[D]{\fnms{Antony} \snm{Williams}},
\author[E]{\fnms{John} \snm{Overington}},
\author[E]{\fnms{Anna} \snm{Gaulton}},

\address[A]{Department of Bioinformatics - BiGCaT, Maastricht University, ADDRESS, Maastricht,\\ The Netherlands\\
E-mail: egon.willighagen@maastrichtuniversity.nl}
\runningauthor{E.L. Willighagen et al.}
\address[B]{Uppsala University}
\address[C]{University of Queensland}
\address[D]{xxx}
\address[E]{European Bioinformatics Institute}

@@

\begin{figure}[t]
\includegraphics[width=0.5\textwidth]{figs/relations}
\caption{The various resource types found in the ChEMBL triples. Some entities are subclasses
of common classes, while others are instances.}\label{f1}
\end{figure}

@@
